Timely Object Recognition

### 2012-11-30 writeups/nips12/poster/poster.tex
mario's suggestions

% Boolean variable: whether or not we want to show grid lines
\newif\ifusegrid
\usegridtrue
\usegridfalse

@@

    % ==============================================================================
    % Title box
    %
    % The following defaults make the title box span the whole top,
    % start 3cm from the top, and end 2 cm from both sides. I have
    % hard-coded the 2s and 3 below.  Play around with the trade-off
    % between changing these numbers and changing
    % ``title-left-margin'' if you are not happy with the defaults.
    \setcounter{title-left-margin}{0} % This specifies the additional padding to the right and left of the title.  Can be negative.
    \setcounter{title-top}{\arabic{total-height}-3} % Places the top of the title 3 cm from the top of the poster.
    \setcounter{title-width}{\arabic{width}-2*\arabic{title-left-margin} - 2*2 - 4} % Automatically calculates the width of the title based on the margin.
    \setcounter{title-left}{\arabic{title-left-margin} + 2} % Automatically places the title 2m from the left edge of the poster + the user specified margin.
    \setcounter{title-box-width}{\arabic{width} - 30}
    \path (\arabic{title-left},\arabic{title-top}) node(title) [style=tbox, text width=\arabic{title-width}cm] {
      \begin{center}

        % Three parboxes allow for images on both sides of the title
        % box with the title text in the middle.
        \parbox{10cm} {
        \includegraphics[width=10cm]{../../figures/berkeley_seal.pdf}
        }
        \parbox{\arabic{title-box-width}cm} {
          \centering
              {\Huge \bf{Timely Object Recognition} } \\
              \vspace{1cm}
              \begin{tabular}{cccc}
                {\huge Sergey Karayev$^1$, \hfill} & {\huge Tobias Baumgartner$^2$, \hfill} & {\huge Mario Fritz$^3$, \hfill} & {\huge Trevor Darrell$^1$}\\
                \multicolumn{4}{c}{\Large $^1$UC Berkeley, $^3$RWTH Aachen, $^3$MPI Informatics}
              \end{tabular}
        }
        \parbox{10cm} {
          % This is just an empty box to make the actual title centered.
          % Add another seal or image if you wish.
          \hspace{1cm}
        }

@@

      \item We use reinforcement learning to learn a \emph{dynamic} policy for selecting detectors and classifiers.

@@

    % ==============================================================================
    % FIGURE 1 WITH EXPLANATION 
    \path (introduction.south west) ++(0cm,-2cm) node(coding) [style=tbox,text width=30cm] {
      \begin{center}
        \includegraphics[width=26cm]{../../figures/figure1_extended.pdf}
      \end{center}

      \begin{itemize}
        \item Potential actions $a \in \mathcal{A}$ are considered according to their predicted \emph{value}.
        \item The value $Q(s,a)$ depends on the \emph{belief state} of the system as well as the action considered.
        \item The selected action returns observations (list of detections, or evaluated feature).
        \item Observations update the belief state through an inference process.
        \item The final evaluation is the area of the AP vs. Time curve between the start time $T_s$ and end time $T_d$.
        \item VOCalues are learned with reinforcement learning, using a reward function derived from this evaluation.
      \end{itemize}

@@

    % ==============================================================================
    % Learning the Policy
    \path (introduction.north east) ++(2cm,0cm) node(model) [style=tbox,text width=34 cm] {
      % \begin{center}
      %   \includegraphics[width=20cm]{../../figures/pomdp_annotated.pdf}
      % \end{center}
      We define our policy as taking an untaken action with maximum value.
      \begin{align*} \pi(s) = \arg\max_{a_i \in \mathcal{A} \setminus \mathcal{O}} Q(s,a_i) = \theta_\pi^\top \phi(s,a) \end{align*}
      The Q-function is linearly approximated.
      \\

      \begin{center}\textbf{Reward Function}\end{center}

      \parbox{20cm}{
      The final performance evaluation of area under the AP vs. Time curve between $T_s$ and $T_d$ is additive per action.
      We define the reward function as
      \begin{align*} R(s^j,a) = \Delta \text{ap} (t_T^j-\frac{1}{2}\Delta t) \end{align*}}
      \parbox{14cm}{
      \begin{center}
        \includegraphics[height=10cm]{../../figures/apvst_expl.pdf}
      \end{center}}
      \\

      \begin{center}\textbf{Reinforcement Learning}\end{center}
      To compute $Q^\pi(s^j,a) = \mathbb{E} [R \mid s, a, \pi)]$, where $R = \sum_{i=j}^J \gamma^{i-j} R(s^i,a^i)$ and $J$ is the index of the last action before deadline time $T_d$, we run Monte Carlo policy iteration.
      We evaluate full episodes of the detection task on several thousand images, with a decreasing $\epsilon$-greedy policy.
      Policy weights $\theta$ are updated with $L_2$ regularization.

@@

@@

    }; \addcenteredtitle{model}{Learning the Policy}

    \parbox{12cm}{
    \textbf{Weights} Learning with a higher $\gamma$ results in policies more relient on the global scene feature, for example.}%
    \parbox{18cm}{\hfill
    \includegraphics[width=17cm]{../../figures/weights.pdf}}
    \\

    \parbox{18cm}{
    \includegraphics[width=17cm]{../../figures/trajectories.pdf}}%\hfill
    \parbox{12cm}{
    \textbf{Trajectories} Action selection traces are plotted in orange over many episodes; the size of the blue circles correspond to the increase in AP obtained by the action. Our policy does not stick a static order but selects actions dynamically to maximize the rewards obtained early on.}
    \\\\

>>>>

% Boolean variable: whether or not we want to show grid lines
\newif\ifusegrid
\usegridtrue
%\usegridfalse

@@

    % ==============================================================================
    % Title box
    %
    % The following defaults make the title box span the whole top,
    % start 3cm from the top, and end 2 cm from both sides. I have
    % hard-coded the 2s and 3 below.  Play around with the trade-off
    % between changing these numbers and changing
    % ``title-left-margin'' if you are not happy with the defaults.
    \setcounter{title-left-margin}{0} % This specifies the additional padding to the right and left of the title.  Can be negative.
    %% TODO: CAN GET 1CM AT TOP HERE  (when the number is -2)
    \setcounter{title-top}{\arabic{total-height}-2} % Places the top of the title 3 cm from the top of the poster.
    \setcounter{title-width}{\arabic{width}-2*\arabic{title-left-margin} - 2*2 - 4} % Automatically calculates the width of the title based on the margin.
    \setcounter{title-left}{\arabic{title-left-margin} + 2} % Automatically places the title 2m from the left edge of the poster + the user specified margin.
    \setcounter{title-box-width}{\arabic{width} - 30}
    \path (\arabic{title-left},\arabic{title-top}) node(title) [style=tbox, text width=\arabic{title-width}cm] {
      \begin{center}

        % Three parboxes allow for images on both sides of the title
        % box with the title text in the middle.
        \parbox{10cm} {
        \includegraphics[height=9cm]{../../figures/berkeley_seal.pdf}
        }
        \parbox{\arabic{title-box-width}cm} {
          \centering
              {\Huge \bf{Timely Object Recognition} } \\
              \vspace{1cm}
              \begin{tabular}{cccc}
                {\huge Sergey Karayev$^1$, \hfill} & {\huge Tobias Baumgartner$^2$, \hfill} & {\huge Mario Fritz$^3$, \hfill} & {\huge Trevor Darrell$^1$}\\\\
                \multicolumn{4}{c}{\Large $^1$UC Berkeley, \hspace{2cm} $^2$RWTH Aachen, \hspace{2cm} $^3$MPI Informatics}
              \end{tabular}
        }
        \parbox{10cm} {
          \includegraphics[width=10cm]{../../figures/MPI_logo.png}
        }

@@

      \item We use reinforcement learning to learn a \emph{dynamic} policy for selecting detectors and classifiers, and learn to take actions that do not provide immediate reward.

@@

    % ==============================================================================
    % FIGURE 1 WITH EXPLANATION 
    \path (introduction.south west) ++(0cm,-2cm) node(coding) [style=tbox,text width=30cm] {
      \begin{center}
        \includegraphics[width=24cm]{../../figures/pomdp_annotated.pdf}
      \end{center}

      \begin{itemize}
        \item An action $a \in \mathcal{A}$ can run detection for an object class $k$ in the whole image, or classify the scene.
        \item Potential actions are considered according to their predicted \emph{value} $Q(s,a)$, which also depends on the \emph{belief state} $s$ of the system.
        \item The selected action returns observations in the form of a list of detections, or simply an evaluated feature.
        \item Observations update the belief state through an inference process.
        \item The final evaluation is the area of the AP vs. Time curve between the start time $T_s$ and end time $T_d$.
      \end{itemize}

      \begin{center}\line(1,0){350}\end{center}

    \begin{center}\textbf{Policy Trajectories}\end{center}

    \parbox{20cm}{
    \includegraphics[width=19cm]{../../figures/trajectories.pdf}}%\hfill
    \parbox{10cm}{
    Action selection traces are plotted over many episodes; the size of the circles correspond to the increase in AP obtained by the action. Our policy selects actions dynamically to maximize the rewards obtained early on.}

@@

    % ==============================================================================
    % Learning the Policy 
    \path (introduction.north east) ++(2cm,0cm) node(model) [style=tbox,text width=34 cm] {
      \begin{center}
        \includegraphics[width=30cm]{../../figures/figure1_extended_hor.pdf}
      \end{center}

      We define our policy as taking an untaken action with maximum value.
      \begin{align*} \pi(s) = \arg\max_{a_i \in \mathcal{A} \setminus \mathcal{O}} Q(s,a_i) = \theta_\pi^\top \phi(s,a) \end{align*}

      The value function
      \begin{align*}Q^\pi(s^j,a) = \mathbb{E} [R \mid s, a, \pi)]\end{align*}
      where $R = \sum_{i=j}^J \gamma^{i-j} R(s^i,a^i)$ and $J$ is the index of the last action before deadline time $T_d$.

      \parbox{20cm}{
      \textbf{Reward Function:} The final performance evaluation of area under the AP vs. Time curve between $T_s$ and $T_d$ is additive per action.
      We define the reward function as
      \begin{align*} R(s^j,a) = \Delta \text{ap} (t_T^j-\frac{1}{2}\Delta t) \end{align*}}
      \parbox{14cm}{
      \begin{center}
        \includegraphics[height=10cm]{../../figures/apvst_expl.pdf}
      \end{center}}
      \\

      \begin{center}\textbf{Reinforcement Learning}\end{center}
      To compute , we run Monte Carlo policy iteration.
      We evaluate full episodes of the detection task on several thousand images, with a decreasing $\epsilon$-greedy policy.
      Policy weights $\theta$ are updated with $L_2$ regularization.

@@

    }; \addcenteredtitle{model}{Learning to Detect on a Budget}

@@

    \parbox{12cm}{
    \textbf{Weights} Learning with a higher $\gamma$ results in policies more relient on the global scene feature, for example.}%
    \parbox{18cm}{\hfill
    \includegraphics[width=17cm]{../../figures/weights.pdf}}
    \\\\
